Robust calibration of numerical models based on relative regret

### 2019-11-18 article-modif-A&E.tex
fix remaining pb when switching from npg -> JCP
add title: 'relative regret', centering of the figures

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

@@

%\arthur{Revoir les notations ($\hat{\bf k}$, ${\bf k}^*$ c'est la meme chose ou pas ? les u, U je ne suis pas sûr que c'est bon non plus)}
%\victor{Pour moi, ce qui est en majuscule, c'est des v.a., et tous les inputs sont en gras (mais on peut laisser tomber le gras)}
\introduction%% \introduction[modified heading if necessary]
%\subsection{Motivation}

@@

A lot of different methods are readily available to solve these minimisation problems. For instance, stochastic Sample Approximation \citep{juditsky_stochastic_2009,kim_guide_2015} is based on a finite and fixed set of samples $\{ \mathbf{u}^{i}\}_{i=1 \dots N}$  of $\mathbf{U}$.
%the sampling of a certain amount of $\mathbf{U}$ 
The estimations are computed using the following expressions {\color{red} plus subtil qu'un calcul empririque ? si oui, expliciter}:
\begin{equation}
\hatkmean = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  J(\mathbf{k},\mathbf{u}^i)
\end{equation}
\begin{equation}
\hatkvar = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  \left( J(\mathbf{k},\mathbf{u}^i) -  \sum_{j=1}^N  J(\mathbf{k},\mathbf{u}^j) \right )^2
\end{equation}
%In the following, the hat notation will indicate an estimator. 
If computationally affordable, one can perform these estimations on a regular grid on $\Kspace \times \Uspace$. In case of expensive computer code, one can build a meta model to ease the minimisation, such as Gaussian processes \citep{janusevskis_simultaneous_2010}.
Even though $\kmean$ is a reasonable choice, there is no guarantee that $J(\kmean, \mathbf{U}=\mathbf{u})$ will not reach catastrophic level for some  $\mathbf{u}$. On the other hand, using $\kvar$ will ensure stability of the cost function, but whithout any control of its level of quality.
%
%For a single $\mathbf{k}$, the value of the cost function is controlled in a probabilistic sense by the mean and variance.
%Chebyshev's inequality gives an upper bound on the probability of being more than $\lambda>0$ units from the mean:
%\begin{equation}
%  \label{eq:cheby_ineq}
%  \Prob_{\mathbf{U}}\left[|J(\mathbf{k}% _{\mathrm{mean}}
%    ,\mathbf{U}) - \mu(\mathbf{k}% _{\mathrm{mean}}
%    )|> \lambda\right] \leq \frac{\sigma^2(\mathbf{k}% _{\mathrm{mean}}
%    )}{\lambda^2}
%\end{equation}
%
Ideally, one would want to have a small mean value, and a small variance as well. Multi-objective optimisation is a proper tool to deal with these simultaneous and sometimes concurrent objectives, for exemple by computing the Pareto front of $\left(\mu(\mathbf{k}),\sigma^2(\mathbf{k})\right)$ as done in~\cite{baudoui_optimisation_2012}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Numerical illustration}
\label{ssec:num_illu}
Before going further in the explanation of our approach, let us illustrate the nature of the 3 previously detailled estimator, $\hatkmean, \hatkvar$ and $\hatkmpe$ on two analytical cost functions. These functions are based on the Branin-Hoo's function, slightly modified to ensure strict positivity:
\begin{align}
  \label{eq:branin_hoo}
 \mathrm{BH}(x_1,x_2) = \frac{1}{51.95}\left[\left(\bar{x}_2 - \frac{5.1 \bar{x}_1^2}{4\pi^2} + \frac{5\bar{x}_1}{\pi} -6 \right)^2 + \left(10 - \frac{10}{8\pi}\right)\cos(\bar{x}_1)-44.81\right]+2\\
\text{with } \bar{x}_1 = 3x_1-5,\quad \bar{x}_2 = 3x_2
\end{align}
%
Using Eq.~\eqref{eq:branin_hoo}, we define the two cost functions on $\Kspace \times \Uspace = [0,5] \times [0,5]$ as:
\begin{align*} J_{\mathrm{BH}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{k},\mathbf{u}) \\
J_{\mathrm{BHswap}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{u},\mathbf{k})
\end{align*}
%We will continue to use $J$ as a generic notation for the cost function, when its use is not specific to the Branin-Hoo function.
Even though the functions are quite similar, the asymmetric roles of $\mathbf{k}$ and $\mathbf{u}$ cause different behaviour.

@@

% as we can argue that both values may be a sensible choice for the MPE. This comes from the fact that the hypothesis that $\mathbf{K}^*$ is a continuous r.v.\ is violated. 
\victor{Réécrit}
A way to avoid this issue is to introduce a bit of leeway for a value to be optimal, or at least ``acceptably not optimal''. This slackness takes the form of a relaxation coefficient, whose choice leads to a new family of robust estimators, along with a measure of their robustness via the coefficient.
%This leads us to the definition of a new family of estimators, for which one can attribute a {\it level of robustness} \elise{je me rend bien compte que cette phrase est un peu bizarre ...mais bon c'est l'idee}

@@

\section{A new family of robust estimators \elise{titre a revoir}}
\label{sec:relax_constraint}
\subsection{Taking the neighborhood into consideration}
The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$. Instead of only considering  optimal values, we propose to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well, as illustrated in Figure~\ref{fig:relax_tuto}. 
To do so, for each $\mathbf{u}$, we define as acceptable values of the cost function, the values that are below $\alpha J^*(\mathbf{u})$, with $\alpha > 1$.

@@

Given that $J>0$, $\Gamma_{\alpha}(\mathbf{k})$ is increasing with respect to $\alpha$ for any $\mathbf{k}\in\Kspace$. We can then focus on the smallest value of $\alpha$ such that $\Gamma_\alpha$ reaches a certain level of confidence $p\in[0,1]$. This leads to the definition of $\checkap$
\begin{align}
  \checkap &= \inf\left\{ \alpha\geq 1 \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\} \nonumber \\
   &= \inf \left\{ \alpha \geq 1 \mid \max_{\mathbf{k}\in\Kspace} \Gamma_{\alpha}(\mathbf{k}) \geq p \right\}   \label{eq:def_alpha_check}
\end{align}
that is the smallest $\alpha$, such that there exists a particular $\checkkp \in \Kspace$ for which $J(\checkkp,\mathbf{U}) \leq \checkap J^*(\mathbf{U})$ with probability $p$. This formulation can be linked to the Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see \cite{rockafellar_deviation_2002}). For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$. The associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$.

@@

\begin{table*}[t]
  \caption{Robust estimators, based on a cost function $J$}
  \label{tab:RO_recap}
\begin{tabular}{lrr}
  \hline
  Definition & Related quantities & Interpretation \\
  \hline
   $\argmin_{\mathbf{k}\in\Kspace} \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kmean$ & Long run performances\\
   $\argmin_{\mathbf{k}\in\Kspace} \Var_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kvar$  & Steady performances\\
   $\argmax_{\mathbf{k}\in\Kspace} p_{\mathbf{K}^*}(\mathbf{k})$ & $\kmpe$ & Most probable minimiser\\
    $\inf\left\{ \alpha \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\}$ & $(p, \checkkp,\checkap)$ & Acceptable values with fixed probability $p$ \\
    $p_{\mathrm{maxratio}} = \argmax p/\checkap$ & $(p_{\mathrm{maxratio}}, \checkk_{\mathrm{maxratio}}, \checka_{\mathrm{maxratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
  \hline
\end{tabular}
\end{table*}

@@

\begin{figure*}[!ht]
\includegraphics[width=12cm]{Figures/branin_side_66_relax_gamma_both.pdf}
\caption{Top: $J_{\mathrm{BH}}$ and $J_{\mathrm{BHswap}}$ contours. The thick yellow lines are the boundaries of the acceptable region defined for $\hat{\checka}_1$, the thick orange are for $\alpha=1.5$. The red dashed line is the estimation $\hat{\checkk}_1$. Bottom: $\hat{\Gamma}_{\alpha}$ for $\alpha = 1.5$ and $\alpha=\hat{\checka}_1$, and estimated density of the minimisers.}
\label{fig:contour_alpha}
\end{figure*}

@@

\begin{figure}[!ht]
\includegraphics[width=12cm]{Figures/alpha_p_BH.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BH}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BH}
\end{figure}

@@

\begin{table*}[!ht]
\centering
\caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
\label{tab:recap_estimates_branin}
\begin{tabular}{lr}
\hline
Estimate & Value \\ \hline
$\hatkvar$ & 1.371 \\ 
$\kest_p,~p=1$ & 1.557 \\ 
$\hatkmean$ & 1.587 \\ 
$\hatkmpe$ & 1.628 \\ 
$\kest_p,~p=0.95$ & 1.672 \\ 
$\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\ \hline
\end{tabular}
\end{table*}

@@

\begin{figure*}[t]
\includegraphics[width=12cm]{Figures/profile_BH_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BH}}$ function, corresponding to the vertical cross sections of the contour. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin}
\end{figure*}

We are now going to shift our focus on the $J_{\mathrm{BHswap}}$ function, as Figure~\ref{fig:ratio_BHs} provides the plots of $p\mapsto \hat{\checka}_p$ and $p\mapsto p/\hat{\checka}_p$.
\begin{figure}[ht]
\includegraphics[width=12cm]{Figures/alpha_p_BHs.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BHswap}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BHs}
\end{figure}

@@

\begin{figure*}[t]
\includegraphics[width=12cm]{Figures/profile_BHs_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BHswap}}$ function. Those profiles are the vertical cross sections of the contours above. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin_switch}
\end{figure*}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=12cm]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}
\begin{table*}[!h]
\centering
\caption{Calibrated values of $\mathbf{k}$ according to different criteria}
\begin{tabular}{lr} \hline
Estimator & Value \\ \hline
$\hatkmpe$ & 0.249 \\
$\kest_{\mathrm{global}}$ & 0.290 \\
$\hat{\mathbf{k}}_{p},~p=1$ & 0.423 \\ 
$\hat{\mathbf{k}}_p,~p=0.90$ & 0.458 \\ 
$\hatkmean$ & 0.501 \\ 
$\hat{\mathbf{k}}_p,~p=0.80$ & 0.505 \\ 
$\hat{\mathbf{k}}_p,~p=0.70$ & 0.560 \\ 
$\hatkvar$ & 0.990\\ \hline
\end{tabular}
\label{tab:recap_estimates_metaSWE}
\end{table*}

@@

\subsubsection{Squared forecast error}
Given two environmental conditions $\mathbf{u}$, used to run the computer simulation and $\mathbf{u}'$, used to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
\begin{equation}
\label{eq:squared_forecast_error}
S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
By averaging over $\mathbf{u}$ and $\mathbf{u}'$ using a Monte-Carlo approximation, we can define the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps.
\begin{equation}
  \label{eq:squared_forecast_error_averaged}
  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
The mean squared forecast error is then averaged over all time-steps between $T$ and $T_{\mathrm{pred}}$, indicating on which point of the domain the forecast error is greater as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
\begin{figure*}[!h]
\centering
\includegraphics[width=12cm]{Figures/forecast_error.pdf}
\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
\label{fig:forecast_squared_error}
\end{figure*}
We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.

Figure~\ref{fig:forecast_squared_error_distrib} shows the distribution of the mean squared error. 
\begin{figure*}[!h]
\centering
\includegraphics[width=10cm]{Figures/forecast_error_distrib_2.pdf}
\caption{Distribution of the forecast squared error, averaged over the different values of the uncertain parameter in the numerical simulations \victor{doublon avec fig.\ref{fig:forecast_squared_error} ?}}
\label{fig:forecast_squared_error_distrib}
\end{figure*}

>>>>

%% For including figures, graphicx.sty has been loxaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

@@

%\arthur{Revoir les notations ($\hat{\bf k}$, ${\bf k}^*$ c'est la meme chose ou pas ? les u, U je ne suis pas sûr que c'est bon non plus)}
%\victor{Pour moi, ce qui est en majuscule, c'est des v.a., et tous les inputs sont en gras (mais on peut laisser tomber le gras)}
%% \introduction[modified heading if necessary]
%\subsection{Motivation}

@@

A lot of different methods are readily available to solve these minimisation problems. For instance, stochastic Sample Approximation \citep{juditsky_stochastic_2009,kim_guide_2015} is based on a finite and fixed set of samples $\{ \mathbf{u}^{i}\}_{i=1 \dots N}$  of $\mathbf{U}$.
%the sampling of a certain amount of $\mathbf{U}$ 
The estimations at a given $\mathbf{k}$ are computed using standard Monte Carlo, resulting in the following optimisation problems:
\begin{equation}
\hatkmean = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  J(\mathbf{k},\mathbf{u}^i)
\end{equation}
and
\begin{equation}
\hatkvar = \argmin_{\mathbf{k} \in \Kspace} \sum_{i=1}^N  \left( J(\mathbf{k},\mathbf{u}^i) -  \sum_{j=1}^N  J(\mathbf{k},\mathbf{u}^j) \right )^2
\end{equation}
%In the following, the hat notation will indicate an estimator. 
If computationally affordable, one can perform these estimations on a regular grid on $\Kspace \times \Uspace$. In case of expensive computer code, one can build a meta model to ease the minimisation, such as Gaussian processes \citep{janusevskis_simultaneous_2010}.
Even though $\kmean$ is a reasonable choice, there is no guarantee that $J(\kmean, \mathbf{U}=\mathbf{u})$ will not reach catastrophic level for some  $\mathbf{u}$. On the other hand, using $\kvar$ will ensure stability of the cost function, but whithout any control of its level of quality.
%
%For a single $\mathbf{k}$, the value of the cost function is controlled in a probabilistic sense by the mean and variance.
%Chebyshev's inequality gives an upper bound on the probability of being more than $\lambda>0$ units from the mean:
%\begin{equation}
%  \label{eq:cheby_ineq}
%  \Prob_{\mathbf{U}}\left[|J(\mathbf{k}% _{\mathrm{mean}}
%    ,\mathbf{U}) - \mu(\mathbf{k}% _{\mathrm{mean}}
%    )|> \lambda\right] \leq \frac{\sigma^2(\mathbf{k}% _{\mathrm{mean}}
%    )}{\lambda^2}
%\end{equation}
%
Ideally, one would want to have a small mean value, and a small variance as well. Multi-objective optimisation is a proper tool to deal with these simultaneous and sometimes concurrent objectives, for exemple by computing the Pareto front of $\left(\mu(\mathbf{k}),\sigma^2(\mathbf{k})\right)$ as done in~\cite{baudoui_optimisation_2012}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Numerical illustration}
\label{ssec:num_illu}
Before going further in the explanation of our approach, let us illustrate the nature of the 3 previously detailled estimator, $\hatkmean, \hatkvar$ and $\hatkmpe$ on two analytical cost functions. These functions are based on the Branin-Hoo's function, slightly modified to ensure strict positivity:
\begin{align}
  \label{eq:branin_hoo}
 \mathrm{BH}(x_1,x_2) &= \frac{1}{51.95}\left[\left(\bar{x}_2 - \frac{5.1 \bar{x}_1^2}{4\pi^2} + \frac{5\bar{x}_1}{\pi} -6 \right)^2 + \left(10 - \frac{10}{8\pi}\right)\cos(\bar{x}_1)-44.81\right]+2\\
&\text{with } \bar{x}_1 = 3x_1-5,\quad \bar{x}_2 = 3x_2
\end{align}
%
Using Eq.~\eqref{eq:branin_hoo}, we define the two cost functions on $\Kspace \times \Uspace = [0,5] \times [0,5]$ as:
\begin{align*} J_{\mathrm{BH}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{k},\mathbf{u}) \\
J_{\mathrm{BHswap}} : (\mathbf{k},\mathbf{u}) \mapsto \mathrm{BH}(\mathbf{u},\mathbf{k})
\end{align*}
%We will continue to use $J$ as a generic notation for the cost function, when its use is not specific to the Branin-Hoo function.
Even though the functions are quite similar, the asymmetric roles of $\mathbf{k}$ and $\mathbf{u}$ cause different behaviour.

@@

% as we can argue that both values may be a sensible choice for the MPE. This comes from the fact that the hypothesis that $\mathbf{K}^*$ is a continuous r.v.\ is violated. 
A way to avoid this issue is to introduce a bit of leeway for a value to be optimal, or at least ``acceptably not optimal''. This slackness takes the form of a relaxation coefficient, whose choice leads to a new family of robust estimators, along with a measure of their robustness via the coefficient.
%This leads us to the definition of a new family of estimators, for which one can attribute a {\it level of robustness} \elise{je me rend bien compte que cette phrase est un peu bizarre ...mais bon c'est l'idee}

@@

\section{Relative regret-based family of estimators}%A new family of robust estimators \elise{titre a revoir}}
\label{sec:relax_constraint}
\subsection{Taking the neighborhood into consideration}
The density of minimisers has been estimated by optimising $\mathbf{k}\mapsto J(\mathbf{k},\mathbf{u})$ over $\Kspace$ for different realisations of $\mathbf{u}$. Instead of only considering  optimal values, we propose to consider their {\it acceptable} neighbourhood in terms of performance of the cost function as well, as illustrated in Figure~\ref{fig:relax_tuto}. 
To do so, for each $\mathbf{u}$, we define as acceptable values of the cost function, the values that are below $\alpha J^*(\mathbf{u})$, with $\alpha > 1$.

@@

Given that $J>0$, $\Gamma_{\alpha}(\mathbf{k})$ is increasing with respect to $\alpha$ for any $\mathbf{k}\in\Kspace$. We can then focus on the smallest value of $\alpha$ such that $\Gamma_\alpha$ reaches a certain level of confidence $p\in[0,1]$. This leads to the definition of $\checkap$
\begin{align}
  \checkap &= \inf\left\{ \alpha\geq 1 \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\} \nonumber \\
   &= \inf \left\{ \alpha \geq 1 \mid \max_{\mathbf{k}\in\Kspace} \Gamma_{\alpha}(\mathbf{k}) \geq p \right\}   \label{eq:def_alpha_check}
\end{align}
that is the smallest $\alpha$, such that there exists a particular $\checkkp \in \Kspace$ for which $J(\checkkp,\mathbf{U}) \leq \checkap J^*(\mathbf{U})$ with probability $p$. This formulation can be linked to the quantiles and Value-at-Risk of the random variable $\max_{\mathbf{k}} \{ \frac{J(\mathbf{k},\mathbf{U})}{J^*(\mathbf{U})}\}$, that is a measure of risk usually applied in the financial sector (see \cite{rockafellar_deviation_2002}). For different levels $p$, and thus different $\alpha_p$, Figure~\ref{fig:illu_alpha_p} shows examples of $\Gamma_{\alpha_p}$. The associated $\mathbf{k}_p$ is then the first value for which $\Gamma_{\alpha_p}$ reaches $p$.

@@

\begin{table*}[t]
  \centering
  \caption{Robust estimators, based on a cost function $J$}
  \label{tab:RO_recap}
\begin{tabular}{lrr}
  \hline
  Definition & Related quantities & Interpretation \\
  \hline
   $\argmin_{\mathbf{k}\in\Kspace} \Ex_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kmean$ & Long run performances\\
   $\argmin_{\mathbf{k}\in\Kspace} \Var_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U})\right]$& $\kvar$  & Steady performances\\
   $\argmax_{\mathbf{k}\in\Kspace} p_{\mathbf{K}^*}(\mathbf{k})$ & $\kmpe$ & Most probable minimiser\\
    $\inf\left\{ \alpha \mid \exists \checkkp \in \Kspace,\, \Gamma_{\alpha}(\checkkp) \geq p \right\}$ & $(p, \checkkp,\checkap)$ & Acceptable values with fixed probability $p$ \\
    $p_{\mathrm{maxratio}} = \argmax p/\checkap$ & $(p_{\mathrm{maxratio}}, \checkk_{\mathrm{maxratio}}, \checka_{\mathrm{maxratio}})$ & Maximal ratio of $p$ and $\checkap$ \\
  \hline
\end{tabular}
\end{table*}

@@

\begin{figure*}[!ht]
  \centering
\includegraphics[width=10cm]{Figures/branin_side_66_relax_gamma_both.pdf}
\caption{Top: $J_{\mathrm{BH}}$ and $J_{\mathrm{BHswap}}$ contours. The thick yellow lines are the boundaries of the acceptable region defined for $\hat{\checka}_1$, the thick orange are for $\alpha=1.5$. The red dashed line is the estimation $\hat{\checkk}_1$. Bottom: $\hat{\Gamma}_{\alpha}$ for $\alpha = 1.5$ and $\alpha=\hat{\checka}_1$, and estimated density of the minimisers.}
\label{fig:contour_alpha}
\end{figure*}

@@

 \begin{figure}[!ht]
   \centering
\includegraphics[width=10cm]{Figures/alpha_p_BH.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BH}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BH}
\end{figure}

@@

\begin{table*}[!ht]
\centering
\caption{Estimation performed for $J_{\mathrm{BH}}$, sorted by value}
\label{tab:recap_estimates_branin}
\begin{tabular}{lr}
\hline
Estimate & Value \\ \hline
$\hatkvar$ & 1.371 \\ 
$\kest_p,~p=1$ & 1.557 \\ 
$\hatkmean$ & 1.587 \\ 
  $\hatkmpe$ & 1.628 \\
  $\kest_{\mathrm{maxratio}},~\hat{p}_{\mathrm{maxratio}}=0.654$ & 1.637 \\
$\kest_p,~p=0.95$ & 1.672 \\ \hline
\end{tabular}
\end{table*}

@@

\begin{figure*}[t]
  \centering
\includegraphics[width=10cm]{Figures/profile_BH_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BH}}$ function, corresponding to the vertical cross sections of the contour. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin}
\end{figure*}

We are now going to shift our focus on the $J_{\mathrm{BHswap}}$ function, as Figure~\ref{fig:ratio_BHs} provides the plots of $p\mapsto \hat{\checka}_p$ and $p\mapsto p/\hat{\checka}_p$.
\begin{figure}[ht]
  \centering
\includegraphics[width=10cm]{Figures/alpha_p_BHs.pdf}
\caption{Evolution of the couples $(p,\checkap)$ and corresponding ratio $p/\checkap$ for the $J_{\mathrm{BHswap}}$ function. The dashed line indicates the level $p$ associated with the highest ratio}
\label{fig:ratio_BHs}
\end{figure}

@@

\begin{figure*}[t]
  \centering
\includegraphics[width=10cm]{Figures/profile_BHs_all_estimates_noku.pdf}
\caption{Profiles of the different estimates for the $J_{\mathrm{BHswap}}$ function. Those profiles are the vertical cross sections of the contours above. The shaded region corresponds to the interval $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$. The red dashed line, corresponding to the values taken by the cost function when the control variable is set to $\mathbf{k}_1$, is always between $[J^*(\mathbf{u}), \hat{\checka}_1 J^*(\mathbf{u})]$ per design.}
\label{fig:profiles_branin_switch}
\end{figure*}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=.7\textwidth]{Figures/RobustSWEmis_plots.pdf}
\caption{Procedure of robust calibration for the shallow water problem. Top: contours of $J$, conditional minimisers and $\{(\mathbf{k},\mathbf{u}) | J(\mathbf{k},\mathbf{u}) = \hat{\alpha}_1 J^*(\mathbf{u})\}$. Middle: Conditional moments and histogram and KDE of the conditional minimisers. Bottom: $\hat{\Gamma}_{\alpha_p}$ for different levels $p$}
\label{fig:estimation_swe}
\end{figure}
\begin{table*}[!h]
\centering
\caption{Calibrated values of $\mathbf{k}$ according to different criteria}
\begin{tabular}{lr} \hline
Estimator & Value \\ \hline
$\hatkmpe$ & 0.249 \\
$\kest_{\mathrm{global}}$ & 0.290 \\
$\hat{\mathbf{k}}_{p},~p=1$ & 0.423 \\ 
$\hat{\mathbf{k}}_p,~p=0.90$ & 0.458 \\ 
$\hatkmean$ & 0.501 \\ 
$\hat{\mathbf{k}}_p,~p=0.80$ & 0.505 \\ 
$\hat{\mathbf{k}}_p,~p=0.70$ & 0.560 \\ 
$\hatkvar$ & 0.990\\ \hline
\end{tabular}
\label{tab:recap_estimates_metaSWE}
\end{table*}

\begin{figure}[!h]
  \centering
  \includegraphics[width=.8\textwidth]{Figures/profile_swe}
  \caption{Profiles for the calibration problem}
  \label{fig:profiles_swe}
\end{figure}

@@

\subsubsection{Squared forecast error}
Given two environmental conditions $\mathbf{u}$, used to run the computer simulation and $\mathbf{u}'$, used to generate the observations, the squared forecast error for the parameter $\mathbf{k}$ is
\begin{equation}
\label{eq:squared_forecast_error}
S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
By averaging over $\mathbf{u}$ and $\mathbf{u}'$ using a Monte-Carlo approximation, we can define the mean squared forecast error, defined on every point of the spatial domain, and at every time-steps.
\begin{equation}
  \label{eq:squared_forecast_error_averaged}
  S(\mathbf{k}) = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} S_{\mathrm{pred}}(\mathbf{k},\mathbf{u},\mathbf{u}') = \frac{1}{N_{\mathbf{u}} N_{\mathbf{u}'}}\sum_{\mathbf{u},\mathbf{u}'\sim \mathbf{U}} \left(\mathcal{M}_{\mathrm{pred}}(\mathbf{k},\mathbf{u}) - \mathcal{M}^{o}_{\mathrm{pred}}(\mathbf{u}')\right)^2
\end{equation}
The mean squared forecast error is then averaged over all time-steps between $T$ and $T_{\mathrm{pred}}$, indicating on which point of the domain the forecast error is greater as seen on the left plot of Figure~\ref{fig:forecast_squared_error}.
\begin{figure*}[!h]
\centering
\includegraphics[width=.9\textwidth]{Figures/forecast_error.pdf}
\caption{Quality of forecast, depending on the calibrated parameter. The left figures show the metric averaged over time, while the right figure show the mean forecast error, averaged over time and space}
\label{fig:forecast_squared_error}
\end{figure*}
We can see that the mean forecast error squared, on the right side, averaged over time and space is the smallest for $\kest_{\mathrm{global}}$, while $\kest_{1.0}$ performs slightly better $\hatkmean$.
\begin{figure}[!h]
  \centering
  \includegraphics[width=.9\textwidth]{Figures/forecast_CRPS}
  \caption{CRPS computed for different calibrated parameters}
  \label{fig:forecast_crps}
\end{figure}

% \begin{figure*}[!h]
% \centering
% \includegraphics[width=10cm]{Figures/distrib_L2norm.pdf}
% \caption{Distribution of the forecast squared error, averaged over the different values of the uncertain parameter in the numerical simulations \victor{doublon avec fig.\ref{fig:forecast_squared_error} ?}}
% \label{fig:forecast_squared_error_distrib}
% \end{figure*}
